Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-11 WRITEUP/ms.tex
commented MR relation; cleanup

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. 
Star symbols are color-coded by
increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}. 
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
%same as \Fig{larsons_single}.
%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
For interpretation of this figure, see discussion in \Sec{MR}.
\label{fig:MR}}
\end{figure*}

@@

% PVE
Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium
to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
\citep{Larson81a, McKee07a}.
Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
the mass-size relation is also known as the constant column density relation and has been
proposed as a fundamental property of molecular clouds on different physical scales.

By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
\begin{equation}
A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we adopt $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
Further discussions on the interpretation of this is provided in \Sec{MR}.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
can be understood by acknowledging the fact that a given MCC in \flower
does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
predictions for CO line emission in the work presented by
\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
that the MCCs in our simulation have lower column densities than the
star-forming cores observed in the Milky Way, which are
observationally well-resolved within an MCC, and indeed, have
sufficient column density to form CO.

In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
This makes sense from simply the fact that smaller MCCs have smaller masses.
However, what does it mean for them to lie on the same locus?

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
%regions of massive \SF.
%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
%  point on that relationship, at the constant $\Sigma$ value.  }
However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
with a certain tracer (e.g., \citealt{Ballesteros11}).
That is, it is solely a result of $\rho\propto M R^{-3}$.
For instance, \citet{Ballesteros02a} show that the density
of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
two-dimensional space; the latter is done in \obs.
When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
% since $M$ would then scale as $R^{3}$.
% naturally display a linear relationship in $\log M - \log R$ plot.

% the widespread in density for a given R.
We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
Following \citet{Ballesteros02a}'s argument, we expect the density 
of MCCs to be independent of the cloud size (since they are identified in 3D-space).
On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$. 
As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
\label{fig:n}}
\vspace{0.5em}
\end{figure}

>>>>

%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
%\caption{
%Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. 
%Star symbols are color-coded by
%increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
%Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}. 
%Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
%Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
%constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
%%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
%%same as \Fig{larsons_single}.
%%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
%%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
%For interpretation of this figure, see discussion in \Sec{MR}.
%\label{fig:MR}}
%\end{figure*}

@@

% PVE
Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium
to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
%\citep{Larson81a, McKee07a}.
%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
%the mass-size relation is also known as the constant column density relation and has been
%proposed as a fundamental property of molecular clouds on different physical scales.
%
%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
%\begin{equation}
%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
%\end{equation}
%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
%\begin{equation}\label{eqn:constantcolumndensity}
%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
%\end{equation}
%where we adopt $\mu = 2.5$ as the mean molecular weight.
%
%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
%Further discussions on the interpretation of this is provided in \Sec{MR}.
%%
%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

%\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
%The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
%by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
%can be understood by acknowledging the fact that a given MCC in \flower
%does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
%our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
%predictions for CO line emission in the work presented by
%\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
%That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
%that the MCCs in our simulation have lower column densities than the
%star-forming cores observed in the Milky Way, which are
%observationally well-resolved within an MCC, and indeed, have
%sufficient column density to form CO.
%
%In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
%This makes sense from simply the fact that smaller MCCs have smaller masses.
%However, what does it mean for them to lie on the same locus?
%
%The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
%an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
%%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
%%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
%%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
%%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
%%regions of massive \SF.
%%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
%%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
%%  point on that relationship, at the constant $\Sigma$ value.  }
%However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
%with a certain tracer (e.g., \citealt{Ballesteros11}).
%That is, it is solely a result of $\rho\propto M R^{-3}$.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$.
%% naturally display a linear relationship in $\log M - \log R$ plot.
%
%% the widespread in density for a given R.
%We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
%As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
%Following \citet{Ballesteros02a}'s argument, we expect the density 
%of MCCs to be independent of the cloud size (since they are identified in 3D-space).
%On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
%we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$. 
%As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
%
%\begin{figure}
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
%\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
%At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
%See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
%For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
%\label{fig:n}}
%\vspace{0.5em}
%\end{figure}
